Disparity peaks - for appendix

### 2018-02-06 analyses/11-appendix-figure-peaks.Rmd
Add viridis library
Tidy and add lines to bins

# Modify data - add midpoints, remove missing data, filter to just three models
data_max2 <- 
  data_max %>%
  mutate(time1 = unlist(z1)) %>%
  mutate(time2 = unlist(z2)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  mutate(bin_type = relevel(data_max$bin_type, ref = 'Stratigraphy')) %>%
  mutate(model = relevel(data_max$model, ref = 'equalbins')) #%>%
  #filter(model == "equalbins" | model == "proximity" | model == "gradual.split")

@@

beck_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  #scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
       axis.text.x = element_blank(),
        #legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size = 14), 
       strip.text.x = element_text(size = 12)) +
  geom_text(data = ann_text, aes(x = 2, y = 10, 
            label = "Beck2012"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

beck_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  #scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size = 14),
       strip.text.x = element_text(size = 12)) +
  geom_text(data = ann_text, aes(x = 2, y = 10, 
            label = "Beck2012"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)
```

@@

# Modify data - add midpoints, remove missing data, filter to just three models
data_max2 <- 
  data_max %>%
  mutate(time1 = unlist(z1)) %>%
  mutate(time2 = unlist(z2)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  mutate(bin_type = relevel(data_max$bin_type, ref = 'stratigraphy')) %>%
  mutate(model = relevel(data_max$model, ref = 'equalbins'))#%>%
  #filter(model == "equalbins" | model == "proximity" | model == "gradual.split")

@@

brusatte_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  #scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
  expand_limits(y = 0) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
       axis.text.x = element_blank(), 
       legend.position = "none", 
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
 geom_text(data = ann_text, aes(x = 2, y = 20, 
            label = "    Brusatte2014"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

brusatte_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  #scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
  expand_limits(y = 0) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none", 
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
 geom_text(data = ann_text, aes(x = 2, y = 20, 
            label = "    Brusatte2014"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)
```

@@

```{r}
bapst_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
 # scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
 geom_text(data = ann_text, aes(x = 2, y = 72, 
            label = "Bapst2016"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

bapst_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  #scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
 geom_text(data = ann_text, aes(x = 2, y = 72, 
            label = "Bapst2016"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)
```

@@

```{r}
wright_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  #scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 expand_limits(y = c(455, 480)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
 geom_text(data = ann_text, aes(x = 2, y = 460, 
            label = " Wright2017"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

wright_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  #scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 expand_limits(y = c(455, 480)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
 geom_text(data = ann_text, aes(x = 2, y = 460, 
            label = " Wright2017"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)   
```

>>>>

# Modify data - add midpoints, remove missing data, filter to just three models
data_max2 <- 
  data_max %>%
  mutate(time1 = unlist(z1)) %>%
  mutate(time2 = unlist(z2)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  mutate(bin_type = relevel(data_max$bin_type, ref = 'Stratigraphy')) %>%
  mutate(model = relevel(data_max$model, ref = 'equalbins'))

@@

beck_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
       axis.text.x = element_blank(),
        #legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size = 14), 
       strip.text.x = element_text(size = 12)) +
  geom_text(data = ann_text, aes(x = 2, y = 10, 
            label = "Beck2012"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

beck_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        #legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size = 14),
       strip.text.x = element_text(size = 12)) +
  geom_text(data = ann_text, aes(x = 2, y = 10, 
            label = "Beck2012"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)
```

@@

# Modify data - add midpoints, remove missing data, filter to just three models
data_max2 <- 
  data_max %>%
  mutate(time1 = unlist(z1)) %>%
  mutate(time2 = unlist(z2)) %>%
  filter(bs.median != 0 & !is.na(bs.median)) %>%
  mutate(bin_type = relevel(data_max$bin_type, ref = 'stratigraphy')) %>%
  mutate(model = relevel(data_max$model, ref = 'equalbins'))

@@

brusatte_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  expand_limits(y = 0) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
       axis.text.x = element_blank(), 
       legend.position = "none", 
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
  geom_text(data = ann_text, aes(x = 2, y = 20, 
            label = "    Brusatte2014"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

brusatte_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  expand_limits(y = 0) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none", 
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
  geom_text(data = ann_text, aes(x = 2, y = 20, 
            label = "    Brusatte2014"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)
```

@@

```{r}
bapst_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
  geom_text(data = ann_text, aes(x = 2, y = 72, 
            label = "Bapst2016"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

bapst_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
  geom_text(data = ann_text, aes(x = 2, y = 72, 
            label = "Bapst2016"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)
```

@@

```{r}
wright_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  expand_limits(y = c(455, 480)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
  geom_text(data = ann_text, aes(x = 2, y = 460, 
            label = " Wright2017"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)

wright_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  geom_segment(aes(y = time1, x = model, yend = time2, xend = model, colour = model), size = 1) +
  facet_wrap(~bin_type, ncol = 3) +
  expand_limits(y = c(455, 480)) +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       axis.text.x = element_blank(),
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) +
  geom_text(data = ann_text, aes(x = 2, y = 460, 
            label = " Wright2017"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1)   
```
